Object-Oriented Internet - Azure Interoperability

### 2020-11-15 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- refine the text and add final content - added and improved UML diagrams

\begin{figure}
      \centering
      \includegraphics{../.Media/StrategyDomainModel.png}
      \caption{Strategy Domain Model}\label{figure.StrategyDomainModel}
\end{figure}

Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept. The domain model for this archetype is presented in the Fig.~\ref*{subs.architecture}. Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \textit{Networking} service of the \textit{Cyber-physical\ node}. Main functionality of this component is to transfer selected data between \textit{Cyber-physical\ network} using \textit{Networking} services of an existing \textit{Cyber-physical\ node} and \textit{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.

@@

\begin{figure}
      \centering
      \includegraphics[width=5cm]{../.Media/UADataApplicationArchitecture.png}
      \caption{Reactive interoperability implementation}\label{figure.UADataApplicationArchitecture}
\end{figure}

@@

@@

Domain model presenting relationship between the Azure \textit{Cloud-based\ front-end} and \textit{Cyber-physical\ node} attached to the \textit{Cyber-physical\ node} is presented in Fig. \ref*{} \textit{Cloud-based Front-end} and Cyber-physical node, PubSub Gateway, Device, Design and development tools

@@

@@

>>>>

\begin{figure}
      \centering
      \includegraphics[width=8cm]{../.Media/StrategyDomainModel.png}
      \caption{Strategy Domain Model}\label{figure.StrategyDomainModel}
\end{figure}

Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept. The domain model for this archetype is presented in the Fig.~\ref*{figure.StrategyDomainModel}. Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \textit{Networking} service of the \textit{Cyber-physical\ node}. Main functionality of this component is to transfer selected data between \textit{Cyber-physical\ network} using \textit{Networking} services of an existing \textit{Cyber-physical\ node} and \textit{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.

@@

\begin{figure}
      \centering
      \includegraphics[width=8cm]{../.Media/UADataApplicationArchitecture.png}
      \caption{Reactive interoperability implementation}\label{figure.UADataApplicationArchitecture}
\end{figure}

@@

\begin{figure}
      \centering
      \includegraphics[width=8cm]{../.Media/ImplementationDomainModel.png}
      \caption{Implementation Architecture}\label{figure.ImplementationDomainModel}
\end{figure}

@@

A generic domain model presenting relationship between the Azure \textit{Cloud-based\ front-end} and \textit{Cyber-physical\ node} attached to the \textit{Cyber-physical\ network} is presented in Fig. \ref*{figure.StrategyDomainModel}. As it was pointed out in the Sect. \ref*{subs.architecture} using OPC UA PubSub the aggregation of nodes by the network is loosely coupled, i.e. nodes can be added and removed from the network dynamically, and nodes may represent mobile data holding assets.

\begin{figure}
      \centering
      \includegraphics[width=\textwidth]{../.Media/ImplementationArchitecture.png}
      \caption{Implementation Architecture}\label{figure.ImplementationArchitecture}
\end{figure}

%) \textit{Cloud-based Front-end} and Cyber-physical node, PubSub Gateway, Device, Design and development tools

@@

\begin{figure}
      \centering
      \includegraphics[width=\textwidth]{../.Media/AzureGateway.png}
      \caption{Implementation Architecture}\label{figure.AzureGateway}
\end{figure}

@@

The propose architecture enable possibility to interconnect the cloud-based services with the Cyber-physical network. This solution is in contrast to to the architecture presented in OPC UA Part 1 and Part 14.
